### 2014-03-02 paper.tex
First paper draft

\documentclass{paper}
\usepackage{authblk}

\title{Slipstream FRP}
\author[*]{Morgan McDermott}
\author[**]{John Carlyle}
\affil[*]{University of flightless dragons}
\affil[**]{University of angry bees}

\begin{document}
\maketitle
abstract goes here
\twocolumn
\section{Introduction}
Lorem ipsum dolor sit amet, consectetur adipisicing elit, sed do eiusmod tempor incididunt ut labore et dolore magna al\
iqua. Ut enim ad minim veniam, quis nostrud exercitation ullamco laboris nisi ut aliquip ex ea commodo consequat. Duis \
aute irure dolor in reprehenderit in voluptate velit esse cillum dolore eu fugiat nulla pariatur. Excepteur sint occaec\
at cupidatat non proident, sunt in culpa qui officia deserunt mollit anim id est laborum.Lorem ipsum dolor sit amet, co\
nsectetur adipisicing elit, sed do eiusmod tempor incididunt ut labore et dolore magna aliqua. Ut enim ad minim veniam,\
 quis nostrud exercitation ullamco laboris nisi ut aliquip ex ea commodo consequat. Duis aute irure dolor in reprehende\
rit in voluptate velit esse cillum dolore eu fugiat nulla pariatur. Excepteur sint occaecat cupidatat non proident, sun\
t in culpa qui officia deserunt mollit anim id est laborum.Lorem ipsum dolor sit amet, consectetur adipisicing elit, se\
d do eiusmod tempor incididunt ut labore et dolore magna aliqua. Ut enim ad minim veniam, quis nostrud exercitation ull\
amco laboris nisi ut aliquip ex ea commodo consequat. Duis aute irure dolor in reprehenderit in voluptate velit esse ci\
llum dolore eu fugiat nulla pariatur. Excepteur sint occaecat cupidatat non proident, sunt in culpa qui officia deserun\
t mollit anim id est laborum.Lorem ipsum dolor sit amet, consectetur adipisicing elit, sed do eiusmod tempor incididunt\
 ut labore et dolore magna aliqua. Ut enim ad minim veniam, quis nostrud exercitation ullamco laboris nisi ut aliquip e\
x ea commodo consequat. Duis aute irure dolor in reprehenderit in voluptate velit esse cillum dolore eu fugiat nulla pa\
riatur. Excepteur sint occaecat cupidatat non proident, sunt in culpa qui officia deserunt mollit anim id est laborum.L\
orem ipsum dolor sit amet, consectetur adipisicing elit, sed do eiusmod tempor incididunt ut labore et dolore magna ali\
qua. Ut enim ad minim veniam, quis nostrud exercitation ullamco laboris nisi utLorem ipsum dolor sit amet, consectetur adipisicing elit, sed do eiusmod tempor incididunt ut labore et dolore magna al\
iqua. Ut enim ad minim veniam, quis nostrud exercitation ullamco laboris nisi ut aliquip ex ea commodo consequat. Duis \
aute irure dolor in reprehenderit in voluptate velit esse cillum dolore eu fugiat nulla pariatur. Excepteur sint occaec\
at cupidatat non proident, sunt in culpa qui officia deserunt mollit anim id est laborum.Lorem ipsum dolor sit amet, co\
nsectetur adipisicing elit, sed do eiusmod tempor incididunt ut labore et dolore magna aliqua. Ut enim ad minim veniam,\
 quis nostrud exercitation ullamco laboris nisi ut aliquip ex ea commodo consequat. Duis aute irure dolor in reprehende\
rit in voluptate velit esse cillum dolore eu fugiat nulla pariatur. Excepteur sint occaecat cupidatat non proident, sun\
t in culpa qui officia deserunt mollit anim id est laborum.Lorem ipsum dolor sit amet, consectetur adipisicing elit, se\
d do eiusmod tempor incididunt ut labore et dolore magna aliqua. Ut enim ad minim veniam, quis nostrud exercitation ull\
amco laboris nisi ut aliquip ex ea commodo consequat. Duis aute irure dolor in reprehenderit in voluptate velit esse ci\
llum dolore eu fugiat nulla pariatur. Excepteur sint occaecat cupidatat non proident, sunt in culpa qui officia deserun\
t mollit anim id est laborum.Lorem ipsum dolor sit amet, consectetur adipisicing elit, sed do eiusmod tempor incididunt\
 ut labore et dolore magna aliqua. Ut enim ad minim veniam, quis nostrud exercitation ullamco laboris nisi ut aliquip e\
x ea commodo consequat. Duis aute irure dolor in reprehenderit in voluptate velit esse cillum dolore eu fugiat nulla pa\
riatur. Excepteur sint occaecat cupidatat non proident, sunt in culpa qui officia deserunt mollit anim id est laborum.L\
orem ipsum dolor sit amet, consectetur adipisicing elit, sed do eiusmod tempor incididunt ut labore et dolore magna ali\
qua. Ut enim ad minim veniam, quis nostrud exercitation ullamco laboris nisi utLorem ipsum dolor sit amet, consectetur adipisicing elit, sed do eiusmod tempor incididunt ut labore et dolore magna al\
iqua. Ut enim ad minim veniam, quis nostrud exercitation ullamco laboris nisi ut aliquip ex ea commodo consequat. Duis \
aute irure dolor in reprehenderit in voluptate velit esse cillum dolore eu fugiat nulla pariatur. Excepteur sint occaec\
at cupidatat non proident, sunt in culpa qui officia deserunt mollit anim id est laborum.Lorem ipsum dolor sit amet, co\
nsectetur adipisicing elit, sed do eiusmod tempor incididunt ut labore et dolore magna aliqua. Ut enim ad minim veniam,\
 quis nostrud exercitation ullamco laboris nisi ut aliquip ex ea commodo consequat. Duis aute irure dolor in reprehende\
rit in voluptate velit esse cillum dolore eu fugiat nulla pariatur. Excepteur sint occaecat cupidatat non proident, sun\
t in culpa qui officia deserunt mollit anim id est laborum.Lorem ipsum dolor sit amet, consectetur adipisicing elit, se\
d do eiusmod tempor incididunt ut labore et dolore magna aliqua. Ut enim ad minim veniam, quis nostrud exercitation ull\
amco laboris nisi ut aliquip ex ea commodo consequat. Duis aute irure dolor in reprehenderit in voluptate velit esse ci\
llum dolore eu fugiat nulla pariatur. Excepteur sint occaecat cupidatat non proident, sunt in culpa qui officia deserun\
t mollit anim id est laborum.Lorem ipsum dolor sit amet, consectetur adipisicing elit, sed do eiusmod tempor incididunt\
 ut labore et dolore magna aliqua. Ut enim ad minim veniam, quis nostrud exercitation ullamco laboris nisi ut aliquip e\
x ea commodo consequat. Duis aute irure dolor in reprehenderit in voluptate velit esse cillum dolore eu fugiat nulla pa\
riatur. Excepteur sint occaecat cupidatat non proident, sunt in culpa qui officia deserunt mollit anim id est laborum.L\
orem ipsum dolor sit amet, consectetur adipisicing elit, sed do eiusmod tempor incididunt ut labore et dolore magna ali\
qua. Ut enim ad minim veniam, quis nostrud exercitation ullamco laboris nisi ut
\end{document}

### 2014-03-03 paper.tex
updated paper

@@
-\documentclass{paper}
+\documentclass[twocolumn]{paper}
 \usepackage{authblk}
@@
 \maketitle
-abstract goes here
-\twocolumn
-\section{Introduction}
-Lorem ipsum dolor sit amet, consectetur adipisicing elit, sed do eiusmod tempor incididunt ut labore et dolore magna al\
-iqua. Ut enim ad minim veniam, quis nostrud exercitation ullamco laboris nisi ut aliquip ex ea commodo consequat. Duis \
-aute irure dolor in reprehenderit in voluptate velit esse cillum dolore eu fugiat nulla pariatur. Excepteur sint occaec\
-at cupidatat non proident, sunt in culpa qui officia deserunt mollit anim id est laborum.Lorem ipsum dolor sit amet, co\
-nsectetur adipisicing elit, sed do eiusmod tempor incididunt ut labore et dolore magna aliqua. Ut enim ad minim veniam,\
- quis nostrud exercitation ullamco laboris nisi ut aliquip ex ea commodo consequat. Duis aute irure dolor in reprehende\
-rit in voluptate velit esse cillum dolore eu fugiat nulla pariatur. Excepteur sint occaecat cupidatat non proident, sun\
-t in culpa qui officia deserunt mollit anim id est laborum.Lorem ipsum dolor sit amet, consectetur adipisicing elit, se\
-d do eiusmod tempor incididunt ut labore et dolore magna aliqua. Ut enim ad minim veniam, quis nostrud exercitation ull\
-amco laboris nisi ut aliquip ex ea commodo consequat. Duis aute irure dolor in reprehenderit in voluptate velit esse ci\
-llum dolore eu fugiat nulla pariatur. Excepteur sint occaecat cupidatat non proident, sunt in culpa qui officia deserun\
-t mollit anim id est laborum.Lorem ipsum dolor sit amet, consectetur adipisicing elit, sed do eiusmod tempor incididunt\
- ut labore et dolore magna aliqua. Ut enim ad minim veniam, quis nostrud exercitation ullamco laboris nisi ut aliquip e\
-x ea commodo consequat. Duis aute irure dolor in reprehenderit in voluptate velit esse cillum dolore eu fugiat nulla pa\
-riatur. Excepteur sint occaecat cupidatat non proident, sunt in culpa qui officia deserunt mollit anim id est laborum.L\
-orem ipsum dolor sit amet, consectetur adipisicing elit, sed do eiusmod tempor incididunt ut labore et dolore magna ali\
-qua. Ut enim ad minim veniam, quis nostrud exercitation ullamco laboris nisi utLorem ipsum dolor sit amet, consectetur adipisicing elit, sed do eiusmod tempor incididunt ut labore et dolore magna al\
-iqua. Ut enim ad minim veniam, quis nostrud exercitation ullamco laboris nisi ut aliquip ex ea commodo consequat. Duis \
-aute irure dolor in reprehenderit in voluptate velit esse cillum dolore eu fugiat nulla pariatur. Excepteur sint occaec\
-at cupidatat non proident, sunt in culpa qui officia deserunt mollit anim id est laborum.Lorem ipsum dolor sit amet, co\
-nsectetur adipisicing elit, sed do eiusmod tempor incididunt ut labore et dolore magna aliqua. Ut enim ad minim veniam,\
- quis nostrud exercitation ullamco laboris nisi ut aliquip ex ea commodo consequat. Duis aute irure dolor in reprehende\
-rit in voluptate velit esse cillum dolore eu fugiat nulla pariatur. Excepteur sint occaecat cupidatat non proident, sun\
-t in culpa qui officia deserunt mollit anim id est laborum.Lorem ipsum dolor sit amet, consectetur adipisicing elit, se\
-d do eiusmod tempor incididunt ut labore et dolore magna aliqua. Ut enim ad minim veniam, quis nostrud exercitation ull\
-amco laboris nisi ut aliquip ex ea commodo consequat. Duis aute irure dolor in reprehenderit in voluptate velit esse ci\
-llum dolore eu fugiat nulla pariatur. Excepteur sint occaecat cupidatat non proident, sunt in culpa qui officia deserun\
-t mollit anim id est laborum.Lorem ipsum dolor sit amet, consectetur adipisicing elit, sed do eiusmod tempor incididunt\
- ut labore et dolore magna aliqua. Ut enim ad minim veniam, quis nostrud exercitation ullamco laboris nisi ut aliquip e\
-x ea commodo consequat. Duis aute irure dolor in reprehenderit in voluptate velit esse cillum dolore eu fugiat nulla pa\
-riatur. Excepteur sint occaecat cupidatat non proident, sunt in culpa qui officia deserunt mollit anim id est laborum.L\
-orem ipsum dolor sit amet, consectetur adipisicing elit, sed do eiusmod tempor incididunt ut labore et dolore magna ali\
-qua. Ut enim ad minim veniam, quis nostrud exercitation ullamco laboris nisi utLorem ipsum dolor sit amet, consectetur adipisicing elit, sed do eiusmod tempor incididunt ut labore et dolore magna al\
-iqua. Ut enim ad minim veniam, quis nostrud exercitation ullamco laboris nisi ut aliquip ex ea commodo consequat. Duis \
-aute irure dolor in reprehenderit in voluptate velit esse cillum dolore eu fugiat nulla pariatur. Excepteur sint occaec\
-at cupidatat non proident, sunt in culpa qui officia deserunt mollit anim id est laborum.Lorem ipsum dolor sit amet, co\
-nsectetur adipisicing elit, sed do eiusmod tempor incididunt ut labore et dolore magna aliqua. Ut enim ad minim veniam,\
- quis nostrud exercitation ullamco laboris nisi ut aliquip ex ea commodo consequat. Duis aute irure dolor in reprehende\
-rit in voluptate velit esse cillum dolore eu fugiat nulla pariatur. Excepteur sint occaecat cupidatat non proident, sun\
-t in culpa qui officia deserunt mollit anim id est laborum.Lorem ipsum dolor sit amet, consectetur adipisicing elit, se\
-d do eiusmod tempor incididunt ut labore et dolore magna aliqua. Ut enim ad minim veniam, quis nostrud exercitation ull\
-amco laboris nisi ut aliquip ex ea commodo consequat. Duis aute irure dolor in reprehenderit in voluptate velit esse ci\
-llum dolore eu fugiat nulla pariatur. Excepteur sint occaecat cupidatat non proident, sunt in culpa qui officia deserun\
-t mollit anim id est laborum.Lorem ipsum dolor sit amet, consectetur adipisicing elit, sed do eiusmod tempor incididunt\
- ut labore et dolore magna aliqua. Ut enim ad minim veniam, quis nostrud exercitation ullamco laboris nisi ut aliquip e\
-x ea commodo consequat. Duis aute irure dolor in reprehenderit in voluptate velit esse cillum dolore eu fugiat nulla pa\
-riatur. Excepteur sint occaecat cupidatat non proident, sunt in culpa qui officia deserunt mollit anim id est laborum.L\
-orem ipsum dolor sit amet, consectetur adipisicing elit, sed do eiusmod tempor incididunt ut labore et dolore magna ali\
-qua. Ut enim ad minim veniam, quis nostrud exercitation ullamco laboris nisi ut
+\section{Abstract}
+We give a definition of \textit{Functional Reactive Programming} (FRP) for use in a javascript based environment that allows for the manipulation of DOM elements and remote servers through the use of sinks and sources in the network.
+There is also an implementation of the FRP network using a DSL to specify the varying layers of the network, this allows a programmer to easily design networks to accomplish tasks by simply specifying the layers and how the layers interact.
+Our implementation builds on previous ones by being more practical, the DSL arises naturally from our definition of FRP and the DSL is simple to use and requires no knowledge of the underlying FRP concepts.
+(END BULLSHIT SALES PITCH)
+
+\section{Introduction to related work}
+Worm Hole paper stuff
+Stream paper stuff
+
+\section{Our contributions}
+pretty much none other than an implementation
+
 \end{document}

### 2014-03-03 paper.tex
About a half page or page of real words

@@
 \usepackage{authblk}
+\usepackage{listings}
+\usepackage{amsmath}
+\lstset{language=Haskell}
 
-\title{Slipstream FRP}
+\title{Usable Functional Reactive Programming with Slipstreams}
 \author[*]{Morgan McDermott}
@@
 Our implementation builds on previous ones by being more practical, the DSL arises naturally from our definition of FRP and the DSL is simple to use and requires no knowledge of the underlying FRP concepts.
-(END BULLSHIT SALES PITCH)
+End sales pitch.
 
-\section{Introduction to related work}
-Worm Hole paper stuff
-Stream paper stuff
+\section{Introduction}
+Functional Reactive Programming is the programming paradigm based on the key concepts of \textit{behaviors} and \textit{reactivity}.
+Behaviors are varying with respect to time and are typically modeled as a stream of values.
+These values can also be considered events depending on the granularity of the stream.
+Reactivity is defined as a reaction to an event, when a node recieves a new value it reacts by changing its value and.
 
@@
 
+and begin from awesome schoools
+
+\section{Terminology}
+\begin{description}
+\item[element] Any value or computation that relys upon previous computations or values.
+An element is analogous to a node in a graph.
+The element is connected to various other elements by means of some function.
+All elements connected to element $e$ can be split into two sets $s_1$ all elements supplying input to $e$ and $s_2$ all elements recieving their input from $e$.
+$s_1$ is called the predecessor set of $e$ or $s_1 = pre(e)$ and $s_2$ is the successor set of $e$ or $s_2 = suc(e)$
+
+\item[signal] It is useful to think of the values being sent from one element to another as a signal being broadcast continuously.
+The element recieving this signal, adjusts its own outgoing signal according to a predefined set of rules, or a function.
+
+\item[behavior] Using the previous definition of an element and a signal, an element can be thought of as a function that maps from one signal to another. More concretly\\
+  $type~element~a~b = Signal ~a \rightarrow Signal ~b$
+
+\item[network] Simply a set of elements that form a connected component. Multiple networks can be used to describe different unrelated components of a particular interface or problem space.
+
+\item[layer] A layer is a set of elements in a network where the intersection of their mutual union of predecessor and sucessor sets is the empty set.
+More formally $\bigcup_{e_i \in L}{pre(e_i)} \cap \bigcup_{e_j \in L}{suc(e_j)} = \emptyset$.
+Breaking a network into layers is helpful because it helps identify dependencies in the network.
+It also helps introduce structure into the environment which can help organize a network which may have been difficult to think about.
+It is not always possible to adhere to the the definition of a layer, or is not practical to do so even if it could be done.
+For example a feedback loop would be by definition a loop on the network, some way of passing a result back to a predacessor.
+This technique is useful for maintaining state in a network amongst other uses.
+
+\item[space-time leak] In a functional reactive service any particular element can depend on values that are far in the past.
+Clearly the longer the program is executing, the longer the history of events, or the longer the stream is.
+A longer stream takes up more memory and can cause slowdown if the stream is not trimmed after a certain point.
+Typically a garbage collection service of some kind is used to clean up old events that no longer being depended on.
+This is analogous to a memory leak in imperative programming.
+The value is said to be a space-time leak if it is unnessisarly being used for computations when it will have no affect on any current elements.
+\end{description}
+
+\begin{thebibliography}{9}
+  \bibitem{wormholes}
+    Daniel Winograd-Cort, Paul Hudak
+    \emph{Wormholes: Introducing Effects to FRP}
+    Yale University
+
+  \bibitem{fran}
+    Conal Elliott and Paul Hudak.
+    \emph{Functional Reactive Animation},
+    http://conal.net/papers/icfp97\\
+    1997
+
+\end{thebibliography}
 \end{document}

### 2014-03-04 paper.tex
Fixed L
Added more schtuff

@@
 \section{Our contributions}
-pretty much none other than an implementation
-
-and begin from awesome schoools
+Merging streams and wormholes and making an implementation of the whole thing practical. And making it based in theory so its not a giant mess like bacon.js. Monad streams woo!
 
@@
 
+\item[network] Simply a set of elements that form a connected component. Multiple networks can be used to describe different unrelated components of a particular interface or problem space.
+
 \item[signal] It is useful to think of the values being sent from one element to another as a signal being broadcast continuously.
@@
 
+\item[stream] An element may have need of signals from more than one timestep in the past.
+A stream is essentially a history of all previous values of a signal, with the most current signal value at the head of the list.
+Streams travel between elements, thus allowing an element to select what timestep it selects a value from.
+The downside of streams is that they allow for spacetime leaks, which are described below.
+
 \item[behavior] Using the previous definition of an element and a signal, an element can be thought of as a function that maps from one signal to another. More concretly\\
-  $type~element~a~b = Signal ~a \rightarrow Signal ~b$
+  $type~element~a~b = Signal ~a \rightarrow Signal ~b$\\
+  Behaviors are typically thought of in terms of continuous functions.
+What FRP is trying to do is model the change in behavior of some element in a network.
+This takes up a lot of processor power  and is not very effecient.
 
-\item[network] Simply a set of elements that form a connected component. Multiple networks can be used to describe different unrelated components of a particular interface or problem space.
+\item[event] An event is a discrete behavior.
+Since behaviors preform so poorly it is often nessisary to break a signal into a set of discrete values.
+The cutoff is not clear between high and low sampling rates.
+With a high sample rate something can be considered a behavior, with a low sample rate it can be considered an event.
 
 \item[layer] A layer is a set of elements in a network where the intersection of their mutual union of predecessor and sucessor sets is the empty set.
-More formally $\bigcup_{e_i \in L}{pre(e_i)} \cap \bigcup_{e_j \in L}{suc(e_j)} = \emptyset$.
+More formally $\bigcup_{e_i \in L}{pre(e_i)} \cap \bigcup_{e_j \in L}{suc(e_j)} = \emptyset$ where $L$ is a layer.
 Breaking a network into layers is helpful because it helps identify dependencies in the network.
@@
 \end{description}
-
+\section{Related work}
+\subsection{High order streams}
+\cite{streams}
+\section{Future work}
+Probably some since we want to keep working on things. I bet it will have to do with extending the language definition and possibly defining streams better.
 \begin{thebibliography}{9}
   \bibitem{wormholes}
-    Daniel Winograd-Cort, Paul Hudak
+    Daniel Winograd-Cort, Paul Hudak.
     \emph{Wormholes: Introducing Effects to FRP}
@@
     Conal Elliott and Paul Hudak. 
-    \emph{Functional Reactive Animation},
-    http://conal.net/papers/icfp97\\
-    1997
+    Functional reactive animation.
+    \emph{In International Conference on Functional Programming},
+    June 1997, pages 263-273.
+
+\bibitem{streams}
+  Gergely Patai.
+  Ecient and Compositional Higher-Order Streams.
+  Budapest University of Technology and Economics, Budapest, Hungary
 

### 2014-03-06 paper.tex
Changes and a bib

@@
 \usepackage{amsmath}
+\usepackage{cite}
+\usepackage[margin=1.0in]{geometry}
 \lstset{language=Haskell}
@@
 \maketitle
+
 \section{Abstract}
@@
 \subsection{High order streams}
-\cite{streams}
 \section{Future work}
 Probably some since we want to keep working on things. I bet it will have to do with extending the language definition and possibly defining streams better.
-\begin{thebibliography}{9}
-  \bibitem{wormholes}
-    Daniel Winograd-Cort, Paul Hudak.
-    \emph{Wormholes: Introducing Effects to FRP}
-    Yale University
 
-  \bibitem{fran}
-    Conal Elliott and Paul Hudak. 
-    Functional reactive animation.
-    \emph{In International Conference on Functional Programming},
-    June 1997, pages 263-273.
-
-\bibitem{streams}
-  Gergely Patai.
-  Ecient and Compositional Higher-Order Streams.
-  Budapest University of Technology and Economics, Budapest, Hungary
-
-\end{thebibliography}
+\bibliography{paper.bib}{}
+\bibliographystyle{plain}
 \end{document}

### 2014-03-06 paper.tex
Stream stuff

@@
 \section{Abstract}
+\cite{ElliottHudak97:Fran}
 We give a definition of \textit{Functional Reactive Programming} (FRP) for use in a javascript based environment that allows for the manipulation of DOM elements and remote servers through the use of sinks and sources in the network.
@@
 The downside of streams is that they allow for spacetime leaks, which are described below.
+A stream of type $Stream~a$ will be denoted as $\langle v_0~v_1~v_2~...\rangle$ where $v_i$ is of type $a$.
 
@@
 \subsection{High order streams}
+\cite{HighOrderStreams}
+\subsection{Wormholes}
+\cite{WinogradCort2012HS}
 \section{Future work}
@@
 
-\bibliography{paper.bib}{}
+\bibliography{paper}
 \bibliographystyle{plain}

### 2014-03-06 paper.tex
Added some more stuff

@@
 Our implementation builds on previous ones by being more practical, the DSL arises naturally from our definition of FRP and the DSL is simple to use and requires no knowledge of the underlying FRP concepts.
-End sales pitch.
 
@@
 Reactivity is defined as a reaction to an event, when a node recieves a new value it reacts by changing its value and.
+A nessisary inclusion from an interface design standpoint is the ability to dynamically change the network.
+
+\section{Example requiring dynamic network}
+In a simple interface with a drop down menu where the drop down elements can change in reaction to a some other form of input.
 
@@
 The downside of streams is that they allow for spacetime leaks, which are described below.
-A stream of type $Stream~a$ will be denoted as $\langle v_0~v_1~v_2~...\rangle$ where $v_i$ is of type $a$.
+A stream of type $Stream~a$ will be denoted as $\langle v_0~v_1~v_2~...\rangle$ where $v_i$ is of type $
+a$.
 
@@
 With a high sample rate something can be considered a behavior, with a low sample rate it can be considered an event.
+Our implementation of FRP is skewed toward events.
 
@@
 \end{description}
+\section{Semantics}
+
+$\frac{}{\langle l<-(@a,...)->...,\sigma \rangle \Downarrow \sigma[l \mapsto Stream ~a]}$ Why is this so hard?
+
 \section{Related work}
 \subsection{High order streams}
-\cite{HighOrderStreams}
+Work has already been done on higher order streams \cite{HighOrderStreams}. Higher order streams are nessisary for having a dynamic network. Dynamic networks are required
 \subsection{Wormholes}

### 2014-03-07 paper.tex
Edited

--- 2014-03-06 paper.tex
@@
 \section{Abstract}
-We give a definition of \textit{Functional Reactive Programming} (FRP) for use in a javascript based environment that allows for the manipulation of DOM elements and remote servers through the use of sinks and sources in the network.
-There is also an implementation of the FRP network using a DSL to specify the varying layers of the network, this allows a programmer to easily design networks to accomplish tasks by simply specifying the layers and how the layers interact.
-Our implementation builds on previous ones by being more practical, the DSL arises naturally from our definition of FRP and the DSL is simple to use and requires no knowledge of the underlying FRP concepts.
-End sales pitch.
+We give a definition of \textit{Functional Reactive Programming} (FRP) that allows for dynamic signal networks and safe interaction with the real world.
+We allow signal networks to be dynamic by modeling them as higher order streams (as in Patai \cite{HighOrderStreams}), and use the concept of wormholes (from Winograd \cite{WinogradCort2012HS}) to make interaction with real world resources safe.
+All signal values are modeled as $Maybe$ values to allow for defined behavior in the face of disrupted signals, and to reference signal values before they have any reasonable value.
+We also specify a DSL that uses this FRP model, allowing a programmer to easily design signal networks to accomplish tasks by specifying layers and how the layers interact.
+Our implementation builds on previous work by being more practical.
+The DSL arises naturally from our definition of FRP, is simple to use and requires only limited knowledge of the underlying FRP concepts.
 
 \section{Introduction}
-Functional Reactive Programming is the programming paradigm based on the key concepts of \textit{behaviors} and \textit{reactivity}.
-Behaviors are varying with respect to time and are typically modeled as a stream of values.
+Functional Reactive Programming, introduced by Fran \cite{ElliottHudak97:Fran}, is the programming paradigm based on the key concepts of \textit{behaviors}, \textit{events}, and \textit{reactivity}.
+Behaviors vary with respect to time and are typically modeled as a stream of values.
 These values can also be considered events depending on the granularity of the stream.
-Reactivity is defined as a reaction to an event, when a node recieves a new value it reacts by changing its value and.
+Reactivity is defined as a reaction to an event; when a node recieves a new value it reacts by changing its value.
+FRP is particularly well suited for transforming data and data structures since it is, by nature, a collection of pure functions.
 
-\section{Our contributions}
-Merging streams and wormholes and making an implementation of the whole thing practical. And making it based in theory so its not a giant mess like bacon.js. Monad streams woo!
+We solve the problem of interacting with time-varying values can be solved using stream-based FRP, where each computation sends a stream instead of a signal value.
+A stream is essentially a complete history of the values of a particular computation.
+Any other computation that needs the current value, or a value from the past, can look at the stream and find the appropriate values.
+This leads to additional problems like memory usage growing out of control as new values are continually added to the stream and not removed.
+In some systems garbage collection finds and removes values from streams that are no longer dependencies for other computations.
+In Elerea \cite{HighOrderStreams}, this is solved by only allowing access to the most recent values in streams.
+
+This paper primarily introduces a way for FRP to interact safely in an environment filled with questionable resources.
+(What the different sections are for) (Section 1) Section 2 Section 3 Section 4 Section 5 Section 6 Section 7.
+
+\section{A Motivating Example}
+Adapting FRP for javascript development would be super fantastic since javascript GUI code deals with varying values all the time.
+In particular the asynchronous communication between a server and client through the use of AJAX can be thought of as a time-varying signal between two nodes.
+
+There are several problems that must be solved in stream-based FRP to allow this transaction to take place.
+First, how do we interact with the environment itself?
+Since we need to manipulate the DOM and perform asynchronous requests, we have to change state.
+
+Secondly, how do we model the changing requirements for interfaces?
+If the user presses a button to submit a query to the server, the server could respond in a way indicating that they need to update the interface on the page.
+Perhaps we need to create more buttons that could perform different server queries.
+In order to solve this, we must define a flexible, dynamic FRP network that can modify itself.
+Elerea solves this by providing Higher Order Streams.
+
+We need to ensure that the time-based values from the server are treated in a well-defined way.
+Namely, what if we have never contacted the server?
+What should the value of its stream be, and how should that differ from the stream after it has responded and is in an idle state again?
+We solve this by encapsulating every stream value in a $Maybe$, as we will explain later.
+
+Lastly, what happens when two computations wish to change the state of the interface at the same time?
+How can we allow safe interaction between external state and multiple FRP calculations that wish to modify the state?
+We solve this using Wormholes as defined by Winograd-Cort \cite{WinogradCort2012HS}
 
@@
 \begin{description}
-\item[element] Any value or computation that relys upon previous computations or values.
+\item[element] Any value or computation that relies upon previous computations or values.
 An element is analogous to a node in a graph.
 The element is connected to various other elements by means of some function.
-All elements connected to element $e$ can be split into two sets $s_1$ all elements supplying input to $e$ and $s_2$ all elements recieving their input from $e$.
-$s_1$ is called the predecessor set of $e$ or $s_1 = pre(e)$ and $s_2$ is the successor set of $e$ or $s_2 = suc(e)$
+All elements connected to element $e$ can be split into two sets $s_1$ (all elements supplying input to $e$) and $s_2$ (all elements recieving their input from $e$).
+$s_1$ is called the predecessor set of $e$ or $s_1 = pre(e)$, and $s_2$ is the successor set of $e$ or $s_2 = suc(e)$
 
-\item[network] Simply a set of elements that form a connected component. Multiple networks can be used to describe different unrelated components of a particular interface or problem space.
+\item[network] A set of elements that form a connected component. Multiple networks can be used to describe different unrelated components of a particular interface or problem space.
 
 \item[signal] It is useful to think of the values being sent from one element to another as a signal being broadcast continuously.
-The element recieving this signal, adjusts its own outgoing signal according to a predefined set of rules, or a function.
+The element receiving this signal adjusts its own outgoing signal according to a predefined set of rules or a function.
 
@@
 The downside of streams is that they allow for spacetime leaks, which are described below.
+A stream of type $Stream~a$ will be denoted as $\langle v_0~v_1~v_2~...\rangle$ where $v_i$ is of type $
+a$.
 
-\item[behavior] Using the previous definition of an element and a signal, an element can be thought of as a function that maps from one signal to another. More concretly\\
+\item[behavior] Using the previous definition of an element and a signal, an element can be thought of as a function that maps from one signal to another. More concretely \\
   $type~element~a~b = Signal ~a \rightarrow Signal ~b$\\
@@
 What FRP is trying to do is model the change in behavior of some element in a network.
-This takes up a lot of processor power  and is not very effecient.
+This takes up a lot of processor power  and is not very efficient.
 
 \item[event] An event is a discrete behavior.
-Since behaviors preform so poorly it is often nessisary to break a signal into a set of discrete values.
+Since behaviors perform so poorly, it is often necessary to break a signal into a set of discrete values.
 The cutoff is not clear between high and low sampling rates.
-With a high sample rate something can be considered a behavior, with a low sample rate it can be considered an event.
+With a high sample rate, something can be considered a behavior; with a low sample rate it can be considered an event.
+Our implementation of FRP is skewed toward events.
 
-\item[layer] A layer is a set of elements in a network where the intersection of their mutual union of predecessor and sucessor sets is the empty set.
+\item[layer] A layer is a set of elements in a network where the intersection of their mutual union of predecessor and successor sets is the empty set.
 More formally $\bigcup_{e_i \in L}{pre(e_i)} \cap \bigcup_{e_j \in L}{suc(e_j)} = \emptyset$ where $L$ is a layer.
 Breaking a network into layers is helpful because it helps identify dependencies in the network.
-It also helps introduce structure into the environment which can help organize a network which may have been difficult to think about.
-It is not always possible to adhere to the the definition of a layer, or is not practical to do so even if it could be done.
-For example a feedback loop would be by definition a loop on the network, some way of passing a result back to a predacessor.
+It also helps introduce structure into the environment, which can help organize a network which may have been difficult to think about.
+It is not always possible to adhere to the definition of a layer, or is not practical to do so (even if it could) be done.
+For example, a feedback loop would be, by definition, a loop on the network, some way of passing a result back to a predecessor.
 This technique is useful for maintaining state in a network amongst other uses.
 
-\item[space-time leak] In a functional reactive service any particular element can depend on values that are far in the past.
-Clearly the longer the program is executing, the longer the history of events, or the longer the stream is.
+\item[space-time leak] In a functional reactive service, any particular element can depend on values that are far in the past.
+Clearly, the longer the program is executing, the longer the history of events, or the longer the stream is.
 A longer stream takes up more memory and can cause slowdown if the stream is not trimmed after a certain point.
-Typically a garbage collection service of some kind is used to clean up old events that no longer being depended on.
+Typically a garbage collection service of some kind is used to clean up old events upon which are no longer being depended..
 This is analogous to a memory leak in imperative programming.
-The value is said to be a space-time leak if it is unnessisarly being used for computations when it will have no affect on any current elements.
+The value is said to be a space-time leak if it is unnecessarily being used for computations when it will have no effect on any current elements.
 \end{description}
+
+\section{Our contributions}
+\subsection{Maybe Streams}
+Merging streams and wormholes and making an implementation of the whole thing practical. Making it based in theory so its not a giant mess like bacon.js. Monad streams woo!
+
+\subsection{Higher-order streams}
+
 \section{Related work}
-\subsection{High order streams}
+
+\subsection{Higher-order streams}
+Work has already been done on higher order streams \cite{HighOrderStreams}. Higher order streams are nessisary for having a dynamic network. Dynamic networks are required
+
+\subsection{Wormholes}
+\cite{WinogradCort2012HS}
 \section{Future work}

### 2014-03-07 paper.tex
Changes made from librry

@@
 
-\title{Usable Functional Reactive Programming with Slipstreams}
+\title{Maybe Slipstreams $|$-o-$|$}
 \author[*]{Morgan McDermott}
@@
 We give a definition of \textit{Functional Reactive Programming} (FRP) that allows for dynamic signal networks and safe interaction with the real world.
-We allow signal networks to be dynamic by modeling them as higher order streams (as in Patai \cite{HighOrderStreams}), and use the concept of wormholes (from Winograd \cite{WinogradCort2012HS}) to make interaction with real world resources safe.
+We allow signal networks to be dynamic by modeling them as higher-order streams (as in Patai \cite{HighOrderStreams}), and use the concept of wormholes (from Winograd \cite{WinogradCort2012HS}) to make interaction with real world resources safe.
 All signal values are modeled as $Maybe$ values to allow for defined behavior in the face of disrupted signals, and to reference signal values before they have any reasonable value.
@@
 In order to solve this, we must define a flexible, dynamic FRP network that can modify itself.
-Elerea solves this by providing Higher Order Streams.
+Elerea solves this by providing Higher-Order Streams.
 
@@
 \section{Our contributions}
+Our contributions are basically jsut reworking the bind in a stream monad to map between layer sets.
+Also each value is wrapped in a maybe, revolutionary.
+This allows safe access to resources that have not yet been created in a dynamic network setting.
+It also allows for safe handling of volatile resources such as HTTP requests or accessing other error prone procedures.
+Convenience elements have been added such as the aggregator, which allows for dynamic seeming networks without any modification to the underlying structure.
+This is possible due to the addition of the maybe value to every stream.
+\subsection{DSL Grammar}
+\footnotesize
+\begin{align*}
+  Statement ::=& ~V \leftarrow Expression &\text{Variable assignment}\\
+  |& ~Expression &\text{Single expression}\\
+  Expression ::=& ~SignalNet &\text{A signal network}\\
+  |& SimpleExpr &\text{An expression}\\
+  SignalNet ::=& ~( Exprs ) \rightarrow SignalNet &\text{Compose layers}\\
+   |& ~(Exprs ) &\text{Single layer} \\
+  Exprs ::=& ~SimpleExpr ~,~ Exprs &\text{List of expressions}\\
+  |& ~SimpleExpr &\text{Single expression}\\
+  SimpleExpr ::=& ~L[``Javascript code''] &\text{Lift}\\
+  |& ~ @V &\text{Get}\\
+  |& ~ *V(SimpleExpr) &\text{Put}\\ 
+  |& ~ V( Exprs ) &\text{Function call}\\
+  V ::=& ~Word~Characters &\text{Variable}
+\end{align*}
+\normalsize
+As you can see our grammar is exteremly simple and contributes basically 1 monad with bind. Thats it. PhD Please.
+
 \subsection{Maybe Streams}
@@
 \subsection{Higher-order streams}
+Streams composed with streams oh my. Gotta look out for those undefined values. The value of composed streams is the diagonal of the matrix formed by the stream values. Boop:
+
+\begin{align*}
+  \langle &\langle \mathbf{v_{00}} ~ v_{01} ~ v_{02} ~ v_{03} ~ ... ~ \rangle \\
+  &\langle \perp ~ \mathbf{v_{11}} ~ v_{12} ~ v_{13} ~... ~ \rangle \\
+  &\langle \perp ~ \perp ~ \mathbf{v_{22}} ~ v_{23} ~ ...  ~ \rangle \rangle
+\end{align*}
+
+Better idea to avoid wasted space and complex ge
+
+\begin{align*}
+  \langle &\langle \mathbf{v_{00}} ~ v_{01} ~ v_{02} ~ v_{03} ~ ... ~ \rangle \\
+  &\langle  \mathbf{v_{11}} ~ v_{12} ~ v_{13} ~ v_{14} ~ ... ~ \rangle \\
+  &\langle  \mathbf{v_{22}} ~ v_{23} ~ v_{24} ~ v_{25} ~ ...  ~ \rangle \rangle
+\end{align*}
 
@@
 \subsection{Higher-order streams}
-Work has already been done on higher order streams \cite{HighOrderStreams}. Higher order streams are nessisary for having a dynamic network. Dynamic networks are required
+Work has already been done on higher-order streams \cite{HighOrderStreams}. Higher-order streams are nessisary for having a dynamic network. Dynamic networks are required
 

### 2014-03-11 paper.tex
Updated intro a little

@@
 
-\title{Maybe Slipstreams $|$-o-$|$}
+\title{Maybe Slipstreams}
 \author[*]{Morgan McDermott}
-\author[**]{John Carlyle}
+\author[*]{John Carlyle}
 \affil[*]{University of flightless dragons}
-\affil[**]{University of angry bees}
 
@@
 \section{Introduction}
-Functional Reactive Programming, introduced by Fran \cite{ElliottHudak97:Fran}, is the programming paradigm based on the key concepts of \textit{behaviors}, \textit{events}, and \textit{reactivity}.
-Behaviors vary with respect to time and are typically modeled as a stream of values.
+\subsection{What is FRP}
+Functional Reactive Programming, introduced by Fran \cite{ElliottHudak97:Fran}, is a programming paradigm based on the key concepts of time varying values.
 These values can also be considered events depending on the granularity of the stream.
@@
 
+\subsection{Why use FRP}
+FRP is a useful approach to user interface design because it is declaritive.
+Most interface design forces you to define exactly how to generate each value.
+With the time varying values supplied by an FRP network the programmer can choose \textit{what} an interface element is rather than how it is generated.
+By comosing these values together a higher-level description of what each
+
+\subsection{Problems with FRP}
 We solve the problem of interacting with time-varying values can be solved using stream-based FRP, where each computation sends a stream instead of a signal value.
@@
 
-This paper primarily introduces a way for FRP to interact safely in an environment filled with questionable resources.
+\subsection{Organization}
+This paper primarily introduces a way for FRP to interact safely in an environment filled with hazerdous resources which are difficult to model as a function of time.
 (What the different sections are for) (Section 1) Section 2 Section 3 Section 4 Section 5 Section 6 Section 7.
@@
 How can we allow safe interaction between external state and multiple FRP calculations that wish to modify the state?
-We solve this using Wormholes as defined by Winograd-Cort \cite{WinogradCort2012HS}
+We solve this using Wormholes as defined by Winograd-Cort \cite{WinogradCort2012HS}.
 

### 2014-03-11 paper.tex
Suppress numbering on abstract

@@
 
-\section{Abstract}
+\section*{Abstract}
 We give a definition of \textit{Functional Reactive Programming} (FRP) that allows for dynamic signal networks and safe interaction with the real world.

### 2014-03-14 paper.tex
article type again with no date, looks better

--- 2014-03-11 paper.tex
@@
-\documentclass[twocolumn]{paper}
-\usepackage{authblk}
+\documentclass[twocolumn,11pt,english]{article}
 \usepackage{listings}
@@
 \usepackage{cite}
+\usepackage[T1]{fontenc}
 \usepackage[margin=1.0in]{geometry}
@@
 \title{Maybe Slipstreams}
-\author[*]{Morgan McDermott}
-\author[*]{John Carlyle}
-\affil[*]{University of flightless dragons}
+\date{}
+\author{
+  Carlyle, John\\
+  \textit{jcarlyle@ucsc.edu}
+  \and
+  McDermott, Morgan\\
+  \textit{mmcdermo@ucsc.edu}
+}
 
@@
 \subsection{What is FRP}
-Functional Reactive Programming, introduced by Fran \cite{ElliottHudak97:Fran}, is a programming paradigm based on the key concepts of time varying values.
-These values can also be considered events depending on the granularity of the stream.
-Reactivity is defined as a reaction to an event; when a node recieves a new value it reacts by changing its value.
-FRP is particularly well suited for transforming data and data structures since it is, by nature, a collection of pure functions.
+Functional Reactive Programming, introduced by Fran \cite{ElliottHudak97:Fran}, is a programming paradigm based on time varying values.
 

### 2014-03-14 paper.tex
Working on the intro some more

@@
 \lstset{language=Haskell}
+
+\addtolength{\topmargin}{-0.5in}
 
@@
 Functional Reactive Programming, introduced by Fran \cite{ElliottHudak97:Fran}, is a programming paradigm based on time varying values.
+The fundamental idea behind it is to allow the programmer to express than ``what'' of a program, and the ``how'' of the program be infered.
+FRP operates by a series of \textit{behaviors}, which are time varying values that react with one another to form a program.
 
 \subsection{Why use FRP}
-FRP is a useful approach to user interface design because it is declaritive.
-Most interface design forces you to define exactly how to generate each value.
+FRP is a useful approach to user interface design because it is declarative.
+Most interface design forces you to define exactly how to generate each value and once the value is generated.
+The common approach leads to extremly messy interface code.
 With the time varying values supplied by an FRP network the programmer can choose \textit{what} an interface element is rather than how it is generated.
-By comosing these values together a higher-level description of what each
+By comosing these values together a higher-level description of what each interface element should be.
+From this declarative structure the relationship between pieces of the interface implicitly emerges, freeing the programmer from having to tediously define exactly how each relationship is enacted.
 

### 2014-03-16 paper.tex
DSL Stuffff

--- 2014-03-14 paper.tex
@@
 \usepackage{amsmath}
+\usepackage{amsfonts}
 \usepackage{cite}
 \usepackage[T1]{fontenc}
+\usepackage{graphicx}
+\usepackage{color}
 \usepackage[margin=1.0in]{geometry}
@@
 \section{Introduction}
+
 \subsection{What is FRP}
@@
 \subsection{Problems with FRP}
-We solve the problem of interacting with time-varying values can be solved using stream-based FRP, where each computation sends a stream instead of a signal value.
+We solve the problem of interacting with time-varying values using stream-based FRP, where each computation sends a stream instead of a signal value.
 A stream is essentially a complete history of the values of a particular computation.
@@
 
-\section{Terminology}
+\section{FRP Terminology}
+
 \begin{description}
-\item[element] Any value or computation that relies upon previous computations or values.
-An element is analogous to a node in a graph.
-The element is connected to various other elements by means of some function.
-All elements connected to element $e$ can be split into two sets $s_1$ (all elements supplying input to $e$) and $s_2$ (all elements recieving their input from $e$).
-$s_1$ is called the predecessor set of $e$ or $s_1 = pre(e)$, and $s_2$ is the successor set of $e$ or $s_2 = suc(e)$
-
-\item[network] A set of elements that form a connected component. Multiple networks can be used to describe different unrelated components of a particular interface or problem space.
-
-\item[signal] It is useful to think of the values being sent from one element to another as a signal being broadcast continuously.
-The element receiving this signal adjusts its own outgoing signal according to a predefined set of rules or a function.
-
-\item[stream] An element may have need of signals from more than one timestep in the past.
-A stream is essentially a history of all previous values of a signal, with the most current signal value at the head of the list.
-Streams travel between elements, thus allowing an element to select what timestep it selects a value from.
-The downside of streams is that they allow for spacetime leaks, which are described below.
-A stream of type $Stream~a$ will be denoted as $\langle v_0~v_1~v_2~...\rangle$ where $v_i$ is of type $
-a$.
 
@@
 
-\item[layer] A layer is a set of elements in a network where the intersection of their mutual union of predecessor and successor sets is the empty set.
-More formally $\bigcup_{e_i \in L}{pre(e_i)} \cap \bigcup_{e_j \in L}{suc(e_j)} = \emptyset$ where $L$ is a layer.
-Breaking a network into layers is helpful because it helps identify dependencies in the network.
-It also helps introduce structure into the environment, which can help organize a network which may have been difficult to think about.
-It is not always possible to adhere to the definition of a layer, or is not practical to do so (even if it could) be done.
-For example, a feedback loop would be, by definition, a loop on the network, some way of passing a result back to a predecessor.
-This technique is useful for maintaining state in a network amongst other uses.
+\item[signal] It is useful to think of the values being sent from one element to another as a signal being broadcast continuously.
+The element receiving this signal adjusts its own outgoing signal according to a predefined set of rules or a function.
+
+\item[stream] An element may have need of signals from more than one timestep in the past.
+A stream is essentially a history of all previous values of a signal, with the most current signal value at the head of the list.
+Streams travel between elements, thus allowing an element to select what timestep it selects a value from.
+The downside of streams is that they allow for spacetime leaks, which are described below.
+A stream of type $Stream~a$ will be denoted as $\langle v_0~v_1~v_2~...\rangle$ where $v_i$ is of type $
+a$.
 
@@
 
-\section{Our contributions}
-Our contributions are basically jsut reworking the bind in a stream monad to map between layer sets.
-Also each value is wrapped in a maybe, revolutionary.
-This allows safe access to resources that have not yet been created in a dynamic network setting.
-It also allows for safe handling of volatile resources such as HTTP requests or accessing other error prone procedures.
-Convenience elements have been added such as the aggregator, which allows for dynamic seeming networks without any modification to the underlying structure.
-This is possible due to the addition of the maybe value to every stream.
-\subsection{DSL Grammar}
-\footnotesize
+\section{Network Dynamism through Higher Order Streams}
+In order to express the dynamic behavior that we need to implement GUIs, the underlying signal network needs to be able to change itself over time.
+We choose to model this dynamism with higher order streams like Patai\cite{HighOrderStreams}.
+This method avoids the time and space leaks that were present in other FRP systems with first class signals/behaviors/events \cite{ElliottHudak97:Fran}.
+
+Patai defines his model in terms of \textit{Denotational Design} developed by Conal Elliot \cite{elliott2009denotational}.
+The core idea Patai leverages is the \textit{Type Class Morphism}, or defining an interface by a combination of its \textit{type} and its \textit{properties}.
+By focusing on the interface, this design strategy allows implementations to be checked for correctness but to otherwise have freedom in their methodology.
+
+The core type in Patai's stream model is \textit{Stream a}, representing a stream of values over time. This is analagous to a Behavior, and in fact has the same type signature: 
+\begin{equation}
+  \textbf{type}~\textit{Stream a} = \mathbb{N} \rightarrow a
+\end{equation}
+Any  s::\textit{Stream a} can be thought of as the stream of values:
+\begin{equation}
+  \langle s_0 s_1 s_2 ... s_n \rangle ~where~ s_i :: a
+\end{equation}
+Initially Patai models these Streams using a \textit{cons} constructor that represents a delay of one timestep.
+However, if we use this stream definition and consider a higher order stream of type \textit{Stream (Stream a)}, we end up with quadratic performance for \textit{join} when we attempt to extract a value from the \textit{Stream (Stream a)}.
+This is fairly obvious if we try to visualize the higher order stream, since the values of $join~s$ where $s$ :: \textit{Stream (Stream a)} are the main diagonal of the stream of streams:
+
 \begin{align*}
-  Statement ::=& ~V \leftarrow Expression &\text{Variable assignment}\\
-  |& ~Expression &\text{Single expression}\\
-  Expression ::=& ~SignalNet &\text{A signal network}\\
-  |& SimpleExpr &\text{An expression}\\
-  SignalNet ::=& ~( Exprs ) \rightarrow SignalNet &\text{Compose layers}\\
-   |& ~(Exprs ) &\text{Single layer} \\
-  Exprs ::=& ~SimpleExpr ~,~ Exprs &\text{List of expressions}\\
-  |& ~SimpleExpr &\text{Single expression}\\
-  SimpleExpr ::=& ~L[``Javascript code''] &\text{Lift}\\
-  |& ~ @V &\text{Get}\\
-  |& ~ *V(SimpleExpr) &\text{Put}\\ 
-  |& ~ V( Exprs ) &\text{Function call}\\
-  V ::=& ~Word~Characters &\text{Variable}
+    \langle &\langle \mathbf{v_{00}} ~ v_{01} ~ v_{02} ~ ... ~ \rangle \\
+    &\langle v_{10} ~ \mathbf{v_{11}} ~ v_{12} ~ ... ~ \rangle \\
+    &\langle v_{20} ~ v_{21} ~ \mathbf{v_{22}} ~  ...  ~ \rangle \rangle
+\end{align*}
+
+To solve this problem, Patai moves away from the \textit{cons} definition of Streams.
+Instead, he creates streams and higher order streams from three primitives: $delay$, $start$, and $generator$.
+He also introduces the type $StreamGen$, which has the same signature as a $Stream$ but is only used to represent higher order streams.
+
+\small
+\begin{equation}
+  \mathbf{type}~\mathit{StreamGen~a} = \mathbb{N} \rightarrow a
+\end{equation}
+\normalsize
+The $delay$ function replaces cons in this new configuration.
+The difference is that instead of returning a $Stream$, it returns a $StreamGen$.
+It functions by returning its first argument at $t = 0$, and the first $Stream~a$ applied to the sample time otherwise.
+For intuition, we've also included the simplified type:
+\small
+\begin{align*}
+dela&y :: a \rightarrow Stream~a \rightarrow StreamGen~(Stream~a)\\
+dela&y :: a \rightarrow (\mathbb{N} \rightarrow a) \rightarrow (\mathbb{N} \rightarrow~(\mathbb{N} \rightarrow~a))\\
+dela&y~x~s~t_{start}~t_{sample} =\\
+&|~t_{start} = t_{sample} = x\\
+&|~t_{start} < t_{sample} = s (t_{sample} - 1)\\
+&|~otherwise ~~~~~~=\perp
 \end{align*}
 \normalsize
-As you can see our grammar is exteremly simple and contributes basically 1 monad with bind. Thats it. PhD Please.
 
-\subsection{Maybe Streams}
-Merging streams and wormholes and making an implementation of the whole thing practical. Making it based in theory so its not a giant mess like bacon.js. Monad streams woo!
+The $start$ function simply gives us a safe way to extract a stream from a stream generator. Given that $delay$ is undefined if $t_{start} > t_{sample}$, a universally safe time for $t_{start}$ is 0.
+\small
+\begin{align*}
+&start :: StreamGen (Stream~a) \rightarrow Stream a\\
+&start g = g~0
+\end{align*}
+\normalsize
 
-\subsection{Higher-order streams}
-Streams composed with streams oh my. Gotta look out for those undefined values. The value of composed streams is the diagonal of the matrix formed by the stream values. Boop:
+However, given $t_{sample}$ there is another safe value: $t_{start} = t_{sample}$. This concept is embodied in the function $generator$: 
+\small
+\begin{align*}
+&generator :: Stream~ (StreamGen a) \rightarrow Stream~a\\
+&generator~g~t_{sample} = g~t_{sample}~t_{sample}
+\end{align*}
+\normalsize
 
+TODO: DISCUSS THE FANCY EFFICIENCIES AND BIND AND JOIN ETC
 \begin{align*}
@@
 
-\section{Related work}
+\section{Real World Interfaces}
+\subsection{Signals as Maybe Streams}
+  Consider modeling a stream of data from a server to a browser GUI.
+There are two situations when the value of this stream might have an undefined value: If the connection between server and browser has not yet been initiated, or if it has been disrupted.
 
-\subsection{Higher-order streams}
-Work has already been done on higher-order streams \cite{HighOrderStreams}. Higher-order streams are nessisary for having a dynamic network. Dynamic networks are required
+To model the two cases of \textit{disruption} and \textit{pre-existence}, we introduce what we call a $Signal$, which is roughly modeled as:
+\begin{equation}
+  \textbf{type}~\textit{Signal a} = Stream (Maybe~a)
+\end{equation}
+
+At any point in time, a $Signal$ may now be defined but have a $Nothing$ value.
+We can now be assured that any system behavior dependent on this value will act in a defined way even given possible disruption.
+
+As in the given motivating example, we could now also reference the current value of a stream of data coming from the server before we ever initiate the connection.
 
@@
 \cite{WinogradCort2012HS}
+
+\section{DSL}
+
+A major roadblock in FRP adoption is its complexity.
+Understandably, FRP implementations attempt to be as expressive as possible.
+Our implementation, for example, extended the basic idea of Elerea and Elm with additional safety measures for real world interaction.
+
+The goal of our DSL is to bridge the gap between a complex, fully expressive FRP system, and something that can be easily used to express a usable FRP program.
+It is intended to rest atop more complicated FRP libraries, enabling access for a new class of end users who want a quick and intuitive interface.
+
+\subsection{DSL Components}
+
+When implementing software with FRP, dependencies between values can be confusing.
+This is why in our DSL, we restrict dependencies by dividing Signal values into \textit{layers}.
+Layers are composed of \textit{elements}, representing time-varying values ($Signal$s) computed from previous values.
+To maintain the desired ease of understanding, elements can only depend on the values of elements from the previous layer.
+
+\begin{figure}[h!]
+  \includegraphics[scale=0.8]{layers.eps}
+\caption{DSL Layers and Elements}
+\label{fig:layers}
+\end{figure}
+
+In Figure~\ref{fig:layers}, arrows represent dependencies.
+Element $e_{22}$, for example, depends on $e_{11}$ and $e_{12}$.
+In this system, the output of the FRP program is defined as the tuple of the values of the elements of the last layer; The output of this FRP program would be $(e_{31}, e_{32}, e_{33})$.
+
+\subsection{DSL Definitions}
+\begin{description}
+\item[element] Any time-varying value, or any computation that relies upon previous computations or values.
+An element is essentially a Signal Function that has arity from 0 to $n$ where $n$ is the size of the previous layer.
+All elements connected to element $e$ can be split into two sets: $s_1$ (all elements supplying input to $e$) and $s_2$ (all elements recieving their input from $e$).
+$s_1$ is called the predecessor set of $e$ or $s_1 = pred(e)$, and $s_2$ is the successor set of $e$ or $s_2 = succ(e)$
+
+\item[network] A set of elements that form a connected component. Multiple networks can be used to describe different unrelated components of a particular interface or problem space.
+
+\item[layer] A layer is a set of elements in a network where the intersection of their mutual union of predecessor and successor sets is the empty set. More formally,
+\begin{equation}
+  \bigcup_{e_i \in L}{pred(e_i)} \cap \bigcup_{e_j \in L}{succ(e_j)} = \emptyset
+\end{equation}
+where $L$ is a layer.
+Breaking a network into layers is helpful because it helps identify dependencies in the network.
+It also helps introduce structure into the environment, which can help organize a network during its development.
+\end{description}
+The DSL defined in this way cannot express many network topologies.
+For example, it cannot express feedback loops, and has no way of passing a result back to a predecessor.
+This technique is useful for maintaining state in a network, and there are many other practical uses for it.
+
+\subsection{DSL Examples}
+The goal of the DSL is to easily express \textit{networks} as we've defined them. To express the network from Figure~\ref{fig:layers}, we would write:
+\begin{center}
+$(e_{11}, e_{12}, e_{13})$
+\\ $\rightarrow (e_{21}, e_{22})$
+\\ $\rightarrow (e_{31}, e_{32}, e_{33})$
+\end{center}
+The elements in layer 1 represent functions of type $() \rightarrow Signal~a$, while the elements in all other layers represent a signal function of any arity, i.e.) $Signal~(a, b, ...
+n) \rightarrow Signal~z$
+
+A program in the actual DSL would therefore have $source$s in the first layer and signal functions or sources elsewhere.
+Builtin functions of type $() \rightarrow Signal~a$ are prefixed by $@$ in our DSL for clarity.
+
+In our DSL, $L[expr]$ represents the lifting of an anonymous function that takes as arguments the values of all elements in the previous layer, and whose body is $expr$. That is, 
+\begin{center}
+$L[\$1 * \$2] \equiv lift (\backslash \$1 ~\$2 \rightarrow \$1 * \$2)$
+\end{center}
+Using these constructs, a specific network with the same topology as Figure~\ref{fig:layers} might be:
+\begin{center}
+$(@mousePosX, @mousePosY, @time)$
+\\ $\rightarrow (L[sum(\$1, \$2)], L[\$3 * 2])$
+\\ $\rightarrow (L[\$1 / 2], L[\$1], L[\$3])$
+\end{center}
+\subsection{DSL Grammar}
+\footnotesize
+\begin{align*}
+  Statement ::=& ~V \leftarrow Expression &\text{Variable assignment}\\
+  |& ~Expression &\text{Single expression}\\
+  Expression ::=& ~SignalNet &\text{A signal network}\\
+  |& SimpleExpr &\text{An expression}\\
+  SignalNet ::=& ~( Exprs ) \rightarrow SignalNet &\text{Compose layers}\\
+   |& ~(Exprs ) &\text{Single layer} \\
+  Exprs ::=& ~SimpleExpr ~,~ Exprs &\text{List of expressions}\\
+  |& ~SimpleExpr &\text{Single expression}\\
+  SimpleExpr ::=& ~L[``Javascript code''] &\text{Lift}\\
+  |& ~ @V &\text{$SF :: () \rightarrow Signal~a$}\\
+  |& ~ !V &\text{Get}\\
+  |& ~ *V(SimpleExpr) &\text{Put}\\ 
+  |& ~ V( Exprs ) &\text{Function call}\\
+  V ::=& ~Word~Characters &\text{Variable}
+\end{align*}
+\normalsize
+
+\subsection{Desugaring}
+This DSL can be desugared to a base that is easily analyzed in the context of the FRP system we've constructed so far. Given the two layer network:
+\small
+\begin{align*}
+(@time, @mousePosX) \rightarrow (L[\$1 * \$2], L[\$1 + \$2])
+\end{align*}
+\normalsize
+If we introduce a function $mtup$ where 
+\small
+\begin{align*}
+mtup~::~(Monad~m) \Rightarrow (m~a, ..., m~n) \rightarrow m (a, ..., n)
+\end{align*}
+\normalsize
+We can desugar this specific example to:
+\small
+\begin{align*}
+l1~=&~(time, mousePosX)
+\\l2~=&
+\\&(\backslash (\$1, \$2) \rightarrow return~ (\$1 * \$2, \$1 + \$2)) \gg = mtup~l1
+\end{align*}
+\normalsize
+\section{Related work}
+
 \section{Future work}

### 2014-03-17 paper.tex
Paper

@@
 \usepackage{color}
+\usepackage{verbatim}
 \usepackage[margin=1.0in]{geometry}
@@
 
-\subsection{What is FRP}
-Functional Reactive Programming, introduced by Fran \cite{ElliottHudak97:Fran}, is a programming paradigm based on time varying values.
-The fundamental idea behind it is to allow the programmer to express than ``what'' of a program, and the ``how'' of the program be infered.
-FRP operates by a series of \textit{behaviors}, which are time varying values that react with one another to form a program.
+Functional Reactive Programming, introduced by Fran \cite{ElliottHudak97:Fran}, is a programming paradigm allowing for the manipulation of time-varying values with pure functions.
+Fran was declarative, allowing the programmer to express the ``what'' of a program with interconnected time-varying values, while inferring the ``how'' the program should be instantiated.
+
+The original implementations of FRP like Fran divided time-varying values into two types: \textit{Events}, or a discrete stream of values modeled by $Event~a:: [a]$, and \textit{Behaviors}, or continuous functions of time modeled as $Behavior~a :: t \rightarrow a$.
+
+Behaviors are always implemented by sampling their value at chosen intervals, since computers perform discrete operations.
+The advantage of behaviors is that their resolution is arbitrary - they have a precise value whenever they are sampled.
+With a low enough sample, rate a behavior could be considered an Event, but generally Events are used to model things that are truly discrete (like mouse clicks), etc.
+
+These first FRP systems allowed the programmer to express higher-order FRP constructs, like Behaviors of Behaviors, but in so doing allowed the user to inadvertently create time and space leaks.
+
+In FRP, it is possible to depend on values that are far in the past.
+Clearly, the longer the program is executing, the longer the history of events.
+If the composition of FRP constructs depends on past values, we accumulate a longer stream that takes up more memory and can cause slowdown if the stream is not trimmed after a certain point.
+
+Consider the function $integral$, that takes a Behavior and integrates over all of its past values. 
+\begin{align*}
+  integral :: Behavior~Int \rightarrow Behavior~Int
+\end{align*}
+If we have higher-order constructs, it would be possible to first calculate this integral at a time $t > 0$ - this would require, however, calculating the initial behavior at all sample times from $0 < t_{sample} < t$.
+
+It is also challenging to determine when past values will never be used.
+Typically a garbage collection service of some kind is used to clean up old events upon which are no longer being used.
+This is analogous to a memory leak in imperative programming.
+Similarly, values are often unnecessarily preserved in memory despite not being used in any current computation.
 
 \subsection{Why use FRP}
-FRP is a useful approach to user interface design because it is declarative.
-Most interface design forces you to define exactly how to generate each value and once the value is generated.
-The common approach leads to extremly messy interface code.
-With the time varying values supplied by an FRP network the programmer can choose \textit{what} an interface element is rather than how it is generated.
-By comosing these values together a higher-level description of what each interface element should be.
-From this declarative structure the relationship between pieces of the interface implicitly emerges, freeing the programmer from having to tediously define exactly how each relationship is enacted.
+ The complexity of modern GUI (Graphical User Interface) code motivates our development of this system.
+FRP is a useful approach to user interface design because it permits the user to declaratively describe the complex interaction between GUI elements.
+Using imperative programming, GUI design is often achieved with callbacks and notifications about interaction events.
+
+The common approach leads to extremely messy user interface code, often dubbed ``callback hell'' in the context of javascript \cite{czaplicki2013asynchronous}.. 
+Using time varying values in an FRP network, the programmer can describe \textit{what} an interface element is rather than how it responds to and changes the environment.
+The user can compose these elements together to achieve a declarative description of the user interface.
+From this structure the relationship between pieces of the interface implicitly emerges, freeing the programmer from having to tediously define exactly how each relationship is enacted.
 
 \subsection{Problems with FRP}
-We solve the problem of interacting with time-varying values using stream-based FRP, where each computation sends a stream instead of a signal value.
+  Current FRP systems have several drawbacks, however.
+In order to avoid time and space leaks, Yampa \cite{hudak2003arrows} introduces arrowized FRP.
+The security is provided, essentially, by making not making FRP constructs first-class.
+Instead of Behaviors and Events, arrowized FRP uses $Signal$s, which take on the type of behaviors:
+\begin{center}
+  $Signal~a:: t \rightarrow a$
+\\$SF~a~b:: Signal~a \rightarrow Signal~b$
+\end{center}
+
+Signals are not first class in arrowized FRP, however.
+The basis of arrowized FRP interface is the $Signal~Function$, referred to by the type $SF~a~b$.
+This system then uses the well understood $Arrow$ structure to compose Signal Functions and create a sort of network of transformation.
+
+The problem with arrowized FRP is that it has a limited ability to express dynamic networks of signal functions.
+In Yampa there are $switch$es that given two signals can choose one of them to output at any given time.
+This, however, is far from the dynamism we need to implement certain GUI constructs.
+
+ In our system, we solve the problem of having first class FRP constructs by using a modified stream-based FRP model\cite{HighOrderStreams}, to obtain the safety of Arrowized FRP and the expressiveness of classical FRP.
 A stream is essentially a complete history of the values of a particular computation.
@@
 \section{A Motivating Example}
-Adapting FRP for javascript development would be super fantastic since javascript GUI code deals with varying values all the time.
-In particular the asynchronous communication between a server and client through the use of AJAX can be thought of as a time-varying signal between two nodes.
+Our goal is to adapt FRP for javascript GUI development, avoiding the horrors of \textit{callback hell}.
+One particular problem that often results in mangled code is asynchronous communication between a server and client through via AJAX.
+In our model, we can think of both the discrete values being sent to the server, and the discrete values being received, as a time-varying value sampled at an appropriate interval.
 
-There are several problems that must be solved in stream-based FRP to allow this transaction to take place.
-First, how do we interact with the environment itself?
-Since we need to manipulate the DOM and perform asynchronous requests, we have to change state.
+There are several problems that must be solved in stream-based FRP to allow us to model this situation accurately.
+First, we need to interact with the environment in a safe way.
+We need to perform asynchronous requests, and in other examples manipulate the DOM, etc, so ultimately we have to somehow change state.
 
 Secondly, how do we model the changing requirements for interfaces?
-If the user presses a button to submit a query to the server, the server could respond in a way indicating that they need to update the interface on the page.
-Perhaps we need to create more buttons that could perform different server queries.
-In order to solve this, we must define a flexible, dynamic FRP network that can modify itself.
-Elerea solves this by providing Higher-Order Streams.
+If the user presses a button to submit a query to the server, the server could respond in a way indicating that interface on the page should be fundamentally changed.
+Perhaps we need to create more buttons that could perform different server queries, or remove some functionality from the GUI.
+In order to solve this, we need a dynamic FRP network that can modify itself.
+
+Classical FRP and Elerea are capable of modeling this situation since they have first-order FRP constructs.
+In our case we would use Elerea's solution of higher-order streams to implement this use case.
 
@@
 What should the value of its stream be, and how should that differ from the stream after it has responded and is in an idle state again?
-We solve this by encapsulating every stream value in a $Maybe$, as we will explain later.
+We solve this problem by encapsulating every stream value in a $Maybe$, as we will explain later.
 
 Lastly, what happens when two computations wish to change the state of the interface at the same time?
-How can we allow safe interaction between external state and multiple FRP calculations that wish to modify the state?
+How can we allow safe interaction between external state and multiple effectful FRP functions that wish to modify the same state?
 We solve this using Wormholes as defined by Winograd-Cort \cite{WinogradCort2012HS}.
-
-\section{FRP Terminology}
-
-\begin{description}
-
-\item[behavior] Using the previous definition of an element and a signal, an element can be thought of as a function that maps from one signal to another. More concretely \\
-  $type~element~a~b = Signal ~a \rightarrow Signal ~b$\\
-  Behaviors are typically thought of in terms of continuous functions.
-What FRP is trying to do is model the change in behavior of some element in a network.
-This takes up a lot of processor power  and is not very efficient.
-
-\item[event] An event is a discrete behavior.
-Since behaviors perform so poorly, it is often necessary to break a signal into a set of discrete values.
-The cutoff is not clear between high and low sampling rates.
-With a high sample rate, something can be considered a behavior; with a low sample rate it can be considered an event.
-Our implementation of FRP is skewed toward events.
-
-\item[signal] It is useful to think of the values being sent from one element to another as a signal being broadcast continuously.
-The element receiving this signal adjusts its own outgoing signal according to a predefined set of rules or a function.
-
-\item[stream] An element may have need of signals from more than one timestep in the past.
-A stream is essentially a history of all previous values of a signal, with the most current signal value at the head of the list.
-Streams travel between elements, thus allowing an element to select what timestep it selects a value from.
-The downside of streams is that they allow for spacetime leaks, which are described below.
-A stream of type $Stream~a$ will be denoted as $\langle v_0~v_1~v_2~...\rangle$ where $v_i$ is of type $
-a$.
-
-\item[space-time leak] In a functional reactive service, any particular element can depend on values that are far in the past.
-Clearly, the longer the program is executing, the longer the history of events, or the longer the stream is.
-A longer stream takes up more memory and can cause slowdown if the stream is not trimmed after a certain point.
-Typically a garbage collection service of some kind is used to clean up old events upon which are no longer being depended..
-This is analogous to a memory leak in imperative programming.
-The value is said to be a space-time leak if it is unnecessarily being used for computations when it will have no effect on any current elements.
-\end{description}
 
@@
 \end{equation}
+Patai makes Stream take on the Monad and Applicative typeclass interfaces, following the strategy of Denotational Design.
 Initially Patai models these Streams using a \textit{cons} constructor that represents a delay of one timestep.
@@
 \normalsize
-
+\begin{comment}
 TODO: DISCUSS THE FANCY EFFICIENCIES AND BIND AND JOIN ETC
@@
 \end{align*}
+\end{comment}
+
+\subsection{Application of the stream model}
+Patai modifies his definition of a stream to $Stream~a :: IO a$ in his implementation, since the time index is implicit.
+Likewise in our model we do not explicitly model time for $Signal$s, and allow Signal Functions to be effectful.
+
+Our $Signal$ Monad fulfills the requirements for $Stream$s: extracting a value from the monad is idempotent (will always produce the same sampled value during the same timestep), and is commutative (the order in which $Signal$s are sampled does not matter).
+
+We avoid space-time leaks just as Elerea does, by disallowing access to previous values of Streams/Signals (and implicitly starting newly created streams at a local time of 0, rather than trying to ``catch up'' with global time).
+
+Unlke Elerea, we do not use $delay$ as a base primitive, instead using $foldp$ as a means of delaying signals to create new signals.
 
@@
 
-To model the two cases of \textit{disruption} and \textit{pre-existence}, we introduce what we call a $Signal$, which is roughly modeled as:
+To model the two cases of \textit{disruption} and \textit{pre-existence}, we introduce what we're calling a $Signal$, which is roughly modeled as:
 \begin{equation}
@@
 \end{equation}
-
 At any point in time, a $Signal$ may now be defined but have a $Nothing$ value.
@@
 
-\subsection{Wormholes}
-\cite{WinogradCort2012HS}
+\subsection{Resources and Wormholes}
+If Signal Functions are allowed to be effectful, the side effects of evaluating an FRP network can be hard to determine.
+Since the values of Signals are sampled at an interval, the difficulty of understanding the effects of the effectful signal functions is further compounded.
+
+Consider the example given by Winograd-Cort\cite{WinogradCort2012HS} - if we have two signal functions that send a value to a speaker, then both get evaluated at every sampling of the signal network.
+The value of the speaker is then dependent on the order of evaluation of signal function nodes in the network, which should be hidden from the user.
+
+To solve this problem, Winograd-Cort introduces \textit{Resource Types} and \textit{Wormholes}.
+Resource Types are a phantom type parameter associated with all signal functions.
+If a signal function interacts with a resource, that resource is added to the set of resource types in its type.
+To compose two signal functions, then, their sets of resources must be disjoint.
+
+This means that two signal functions can only be composed if they don't access any of the same resources.
+This idea of restricting access to physical resources is extended to ``virtual resources'' (values in memory) with the concept of \textit{Wormholes}.
+A Wormhole consists of a Blackhole, into which data may be written, and an associated Whitehole, out of which data may be read.
+
+Since this effectively gives the user mutable memory, in order to keep the meaning of programs clear, resource types are used to ensure that no two composed signal functions write to the same Blackhole.
+
+\subsection{Implementing Safe Resources}
+In our FRP system, management of resource types is given to low-level libraries.
+We model both wormholes and access to physical resources as effectful signal functions - that is, sending input to an effectful signal function is equivilant to sending information to a blackhole, and extracting information from it is equivilant to extracting information from a whitehole.
+
+To interact with a speaker, we could have the following effectful Signal Function:
+\small
+\begin{align*}
+  speakerValue~::~SpeakerID \rightarrow SF~Value~Value
+\end{align*}
+\normalsize
+
+The function $speakerValue$ would return a signal function of type $SF~Value~Value$ tagged by the resource type $Speaker \times \{SpeakerID\}$.
+
+This tag only restricts what functions may be composed with speakerValue ($f \circ speakerValue~ID$), and not what functions speakerValue may be composed with ($speakerValue~ID \circ f$).
+
+Since our FRP system will not be implemented in an environment with a strong type system, resource types are checked at runtime during signal function composition (But before evaluation of the signal network).
 
@@
 
+Because of this, our DSL does not directly permit the user to create effectful signal functions tagged with resource types.
+Instead, the user can use a number of precreated libraries, or create their own library and use the DSL atop their implementation.
+
 \subsection{DSL Components}
@@
 Layers are composed of \textit{elements}, representing time-varying values ($Signal$s) computed from previous values.
-To maintain the desired ease of understanding, elements can only depend on the values of elements from the previous layer.
+To maintain the desired ease of understanding, elements can only depend on the values of elements from the previous
 
@@
 
+\begin{comment}
+\begin{description}
+\item[behavior] Using the previous definition of an element and a signal, an element can be thought of as a function that maps from one signal to another. More concretely \\
+  $type~element~a~b = Signal ~a \rightarrow Signal ~b$\\
+  Behaviors are typically thought of in terms of continuous functions.
+What FRP is trying to do is model the change in behavior of some element in a network.
+This takes up a lot of processor power  and is not very efficient.
+
+\item[event] An event is a discrete behavior.
+Since behaviors perform so poorly, it is often necessary to break a signal into a set of discrete values.
+The cutoff is not clear between high and low sampling rates.
+With a high sample rate, something can be considered a behavior; with a low sample rate it can be considered an event.
+Our implementation of FRP is skewed toward events.
+
+\item[signal] It is useful to think of the values being sent from one element to another as a signal being broadcast continuously.
+The element receiving this signal adjusts its own outgoing signal according to a predefined set of rules or a function.
+
+\item[stream] An element may have need of signals from more than one timestep in the past.
+A stream is essentially a history of all previous values of a signal, with the most current signal value at the head of the list.
+Streams travel between elements, thus allowing an element to select what timestep it selects a value from.
+The downside of streams is that they allow for spacetime leaks, which are described below.
+A stream of type $Stream~a$ will be denoted as $\langle v_0~v_1~v_2~...\rangle$ where $v_i$ is of type $
+a$.
+\end{description}
+\end{comment}
 \subsection{DSL Definitions}
 \begin{description}
+
 \item[element] Any time-varying value, or any computation that relies upon previous computations or values.
@@
 It also helps introduce structure into the environment, which can help organize a network during its development.
+
 \end{description}
+
 The DSL defined in this way cannot express many network topologies.
@@
 This technique is useful for maintaining state in a network, and there are many other practical uses for it.
+As we will show, our DSL provides builtin primitives to enable these behaviors.
 
@@
   |& ~SimpleExpr &\text{Single expression}\\
-  SimpleExpr ::=& ~L[``Javascript code''] &\text{Lift}\\
+  SimpleExpr ::=& ~L[Expr] &\text{Lift}\\
   |& ~ @V &\text{$SF :: () \rightarrow Signal~a$}\\
-  |& ~ !V &\text{Get}\\
-  |& ~ *V(SimpleExpr) &\text{Put}\\ 
+  |& ~ (V, V) &\text{Tuple}\\
   |& ~ V( Exprs ) &\text{Function call}\\
+  |& ~ foldp( @V, V, [Expr] ) &\text{Past-Dependent Signal}\\
+  |& ~ Aggregator &\text{New Aggregator}\\
+  |& ~ agg(V, V)&\text{Aggregation}\\
+  |& ~ join(@V)&\text{Monadic Join}\\
   V ::=& ~Word~Characters &\text{Variable}
@@
 \normalsize
-\section{Related work}
+
+\section{Primitives}
+\subsection{Past Dependent Signals}
+ In order to reference past values of signals, we use \textit{foldp} as in Elm. 
+\begin{align*}
+foldp :: SF~a~b \rightarrow (b \rightarrow c) \rightarrow b \rightarrow c
+\end{align*}
+This construct allows us to safely form feedback loops, as well as delay values for one timestep. We can define loop in terms of foldp:
+\begin{align*}
+loop& :: SF~a~b \rightarrow b \rightarrow c
+\\loop&~sf~x0~= foldp~sf~(\backslash x \rightarrow x)~x0
+\end{align*}
+
+\subsection{Aggregation}
+ We need resource typing to ensure we don't send simultaneous signals to the same resource.
+This is an issue only because sending a signal to a resource has undefined behavior when combined with other signals.
+There is a very useful case, however, when we want to combine multiple varying signals together dynamically.
+
+For the static case, we have the combine combinator: 
+\begin{align*}
+combine :: [Signal~a] \rightarrow Signal~[a]
+\end{align*}
+However, what if we have a dynamic collection of things, not known at runtime, that we would like to aggregate together from a variety of sources?
+In this case we can use aggregators.
+An Aggregator allows an arbitrary number of signals to be connected to it at runtime, collecting the values from all connected signals in a list at each timestep.
+Conveniently, we can eliminate values we no longer want by filtering values that become $Nothing$.
+\begin{align*}
+(A, A_{out}) &\leftarrow Aggregator
+\\t &\leftarrow (@time) \rightarrow (L[agg(A, \$1)])
+\end{align*}
+In this trivial example, the value of $A_{out}$ is a list in which the value of every element is the current time, with the same length as the number of timesteps at which the network has been evaluated.
+
+\section{Implementation}
+We implement our FRP system using a \textit{signal graph}, much like Elm does \cite{czaplicki2013asynchronous}.
+Each node in the graph represents a signal function, and the connections between nodes represent values from signal functions being fed into other functions.
+
+The values of these nodes are evaluated at every time step, given a user defined time resolution.
+
+Many FRP implementations are slow for large signal networks.
+Our system allows for signal networks to dynamically modify themselves, so our system must perform well given a large number of signal nodes.
+
+\subsection{Evaluate by need}
+In the na\"ive implementation, every signal function is evaluated at every time step.
+We implement the simple optimization used by many other systems \cite{hudak2003arrows} \cite{czaplicki2013asynchronous} by re-evaluating a signal function node if and only iff the nodes connected to it have been re-evaluated.
+Nodes without dependencies (resources, builtins, or constant functions) then serve as roots in the signal function network.
+The network is topologically sorted, and evaluation follows the connections in the graph.
+
+This leads to interesting semantics for effectful functions.
+If an effectful signal function's input nodes haven't changed, the signal function is not evaluated, and its side-effects are never performed.
+
+\subsection{Asynchronous Resources}
+  Real world resources like HTTP requests may not yield values precisely at each time step of evaluation.
+In our system, the values produced by these resources are fed into an async input buffer and represented by \textit{async} nodes in the signal graph.
+
+At each timestep, async nodes are updated with their most recent value from the async input buffer.
+If there has been no update, then their value remains the same and they are not considered to have been re-evaluated (nodes that depend on them will not be forced to update).
+
+\subsection{Asynchronous Evaluation}
+One of the primary benefits of Elm \cite{czaplicki2013asynchronous} is that it allows long computations in signal functions to evaluate asynchronously - that is, it allows nodes relying on that signal function's value to update on timesteps while the signal function is evaluating.
+
+Our system inherently also permits this through use of the async nodes already in use for real world resources.
+An async signal function node will operate as expected, yielding its last produced value at every time step, updating this value when its computation finishes.
+
+Due to the complexity of these operations, we leave them out of the DSL, although libraries may use them to optimize their performance.
 
@@
 
+\section{Conclusion}
+
+\newpage
+\newpage
 \bibliography{paper}

### 2014-03-17 paper.tex
fixed some stuff

@@
 Functional Reactive Programming, introduced by Fran \cite{ElliottHudak97:Fran}, is a programming paradigm allowing for the manipulation of time-varying values with pure functions.
-Fran was declarative, allowing the programmer to express the ``what'' of a program with interconnected time-varying values, while inferring the ``how'' the program should be instantiated.
+Fran was declarative, allowing the programmer to express the ``what'' of a program with interconnected time-varying values, which implies ``how'' the program should be instantiated.
 
@@
 It is also challenging to determine when past values will never be used.
-Typically a garbage collection service of some kind is used to clean up old events upon which are no longer being used.
+Typically a garbage collection service is used to clean up old events which are no longer dependencies.
 This is analogous to a memory leak in imperative programming.
@@
 The user can compose these elements together to achieve a declarative description of the user interface.
-From this structure the relationship between pieces of the interface implicitly emerges, freeing the programmer from having to tediously define exactly how each relationship is enacted.
+From this structure, the relationship between pieces of the interface implicitly emerges, freeing the programmer from having to tediously define exactly how each relationship is enacted.
 
 \subsection{Problems with FRP}
-  Current FRP systems have several drawbacks, however.
+  Current FRP systems have several drawbacks.
 In order to avoid time and space leaks, Yampa \cite{hudak2003arrows} introduces arrowized FRP.
-The security is provided, essentially, by making not making FRP constructs first-class.
+The security is provided by not making FRP constructs first-class.
 Instead of Behaviors and Events, arrowized FRP uses $Signal$s, which take on the type of behaviors:
@@
 Our goal is to adapt FRP for javascript GUI development, avoiding the horrors of \textit{callback hell}.
-One particular problem that often results in mangled code is asynchronous communication between a server and client through via AJAX.
+One particular problem that often results in mangled code is asynchronous communication between a server and client through AJAX.
 In our model, we can think of both the discrete values being sent to the server, and the discrete values being received, as a time-varying value sampled at an appropriate interval.
 
-There are several problems that must be solved in stream-based FRP to allow us to model this situation accurately.
-First, we need to interact with the environment in a safe way.
-We need to perform asynchronous requests, and in other examples manipulate the DOM, etc, so ultimately we have to somehow change state.
+In order to model this situation we need to augment stream basd FRP.
+Streams need to interact with the environment in a safe way.
+For example streams also need to be able to model asynchronous requests.
 
-Secondly, how do we model the changing requirements for interfaces?
-If the user presses a button to submit a query to the server, the server could respond in a way indicating that interface on the page should be fundamentally changed.
+We need to model the changing requirements for interfaces.
+If the user presses a button to submit a query to the server, the server could respond by indicating that interface on the page should be fundamentally changed.
 Perhaps we need to create more buttons that could perform different server queries, or remove some functionality from the GUI.
@@
 Layers are composed of \textit{elements}, representing time-varying values ($Signal$s) computed from previous values.
-To maintain the desired ease of understanding, elements can only depend on the values of elements from the previous
+To maintain the desired ease of understanding, elements can only depend on the values of elements from the previous layer.
 
@@
 For example, it cannot express feedback loops, and has no way of passing a result back to a predecessor.
-This technique is useful for maintaining state in a network, and there are many other practical uses for it.
+This technique is useful for maintaining state in a network.
 As we will show, our DSL provides builtin primitives to enable these behaviors.
